%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Upnid} % Organization
    {Rio de Janeiro - Brazil} % Location
    {May. 2019 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented RESTful API server for car rental booking application(CARPLAT in Google Play).}
        \item {Built and deployed overall service infrastructure utilizing Docker container, CircleCI, and several AWS stack(Including EC2, ECS, Route 53, S3, CloudFront, RDS, ElastiCache, IAM), focusing on high-availability, fault tolerance, and auto-scaling.}
        \item {Developed an easy-to-use Payment module which connects to major PG(Payment Gateway) companies in Korea.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Agile Content} % Organization
    {São Paulo, Brazil} % Location
    {Sep. 2018 - May. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented APIs that use the SMPP protocol to send and receive text messages,}
        \item {Maintained and implemented new features in RESTful and serverless APIs for different purposes.}
        \item {Built and maintained overall service infrastructure using Docker, Travis and AWS.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {eMiolo.com} % Organization
    {Juiz de Fora, Brazil} % Location
    {Dec. 2017 - May. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed modern backend systems for various web apps using Node.js.}
        \item {Built continuous delivery pipelines for both front-end and back-end applications using Netlify and Travis.}
        \item {Implemented integration and unit testing on several Node.js applications using Mocha and Chai.}
        \item {Developed an internal Slack bot for employees to clock in, integrated with a custom Google Assistant application.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {U\&M Mining and Construction} % Organization
    {Intern} % Location
    {Jun. 2017 - Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed several systems for internal use with React, Node.js and Express.}
        \item {Implemented unit tests using Chai and Mocha.}
        \item {Implemented continuous delivery to new and legacy projects using Travis.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
